\documentclass[a4paper,10pt]{article}
    \usepackage{fullpage}
    \usepackage{enumitem}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[margin=0.9in]{geometry}
    \textheight=10.1in
    \pagestyle{empty}
    %\cfoot{}
    \raggedright
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,linkcolor=darkblue,urlcolor=darkblue,anchorcolor=darkblue,citecolor=darkblue}
    \usepackage{relsize}
\newcommand\Cpp{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-3}{\textbf{++}}}}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}
%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Dolan Murvihill}}\\
    Results-oriented leader with a passion for delivering business success by making great software
\end{center}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
  27 Marney St. \#2       & \hspace{8mm}503 830 4363 \\
  Cambridge, MA 02141      & \hspace{8mm}\url{https://github.com/dmurvihill}     
\end{tabular*}\\
\vspace{1mm}
%==== Education ====%
\header{Education}
\textbf{Worcester Polytechnic Institute (WPI)}\hfill Worcester, MA\\
BS, Computer Science, May 2015\\
\vspace*{1mm}
%==== Work Experience ====%
\header{Experience}
\textbf{EverQuote} \hfill Cambridge, MA\\
\textit{Senior Quantitative Software Engineer} \hfill 2017-2018\\
\textit{Quantitative Software Engineer} \hfill 2015-2017\\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Co-creator and architect of the EverQuote \href{https://en.wikipedia.org/wiki/Real-time_bidding}{Real-Time Bidder}, a high-throughput real-time ad buyer, and its associated data pipeline.
  \item Participated in every part of the software life cycle: AWS
  environment setup, designing and writing the code, deployment,
  managing operational issues.
  \item Managed an intern who delivered a new ad server that is now generating
  record revenue numbers (such as delivering 89\% of display revenue on
  one of our top five revenue days ever).
  \item Successfully agitated to adopt industry-standard software development
  practices such as staging environments, unit tests, and daily
  stand-up.
  \item Recognized department-wide as an advocate for clean software design
  and high code quality.
\end{itemize}
\vspace*{1mm}
 
%==== Volunteer Experience ====%
\header{Volunteer Experience}
\textbf{Voter Choice Massachusetts} \hfill Boston, MA\\
\textit{Director of Regions} \hfill 2017-present\\
\begin{itemize} \itemsep -1pt
\item Oversee our grassroots movement's progress toward a 2020 ballot initiative to adopt 
  \href{http://www.fairvote.org/rcv}{Ranked Choice Voting} in Massachusetts.
\item Support and advise six regional chapters across the state: North
  Shore, Greater Boston, Central MA, Pioneer Valley, Greater Lowell, Cape and Islands.
\item Identify talented volunteer leaders and help them establish new
  chapters.
\item Direct the development of high-production-value strategy literature
  for local chapters.
  \end{itemize}
\textit{Director of Live Outreach} \hfill 2016-2017\\
  \begin{itemize} \itemsep -2pt
  \item Oversaw field outreach across five regions, involving 30 volunteers at over 12 events each month, resulting in 25x growth year over year:\
  \begin{tabular*}{\textwidth}{l r r}
   & \textbf{Nov. 2016} & \textbf{Nov. 2017}\\
  Supporters & 250 & 8000\\
  Volunteers & 50 & 1400\\
  Active Volunteers & 3 & 100\\
  \end{tabular*}
  \item managed four directs and three peers located in Boston, Springfield, Worcester, Lowell, and Dartmouth.\\
  \item Led a 30-volunteer outreach team at the 2017 Democratic State Convention that was instrumental in adding RCV to the Massachusetts Democratic Party platform.
  \end{itemize}

%==== Skills ====%
\header{Skills}
\begin{itemize} \itemsep -2pt
    \item EverQuote management training program graduate
    \item Spreadsheet wizard
    \item Black Belt
    \item Always gets the geography questions at trivia night.
    \end{itemize}
\end{document}
